Cross-Validation Default

### 2023-07-11 minos/testing/auditc.Rmd
Added alcohol to the physical wellbeing model and module, and updated handovers and cross_validation with more plots

final.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
final.dat <- do.call(rbind, lapply(final.files, read.csv)) 
```

@@

>>>>

final.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
final.dat <- do.call(rbind, lapply(final.files, read.csv))

cv.files <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
cv.dat <- do.call(rbind, lapply(final.files, read.csv))
```

@@

```{r}
cv <- cv.dat %>%
  dplyr::select(pidp, time, auditc) %>%
  dplyr::filter(time >= 2015) %>%
  dplyr::filter(time != 2016, time != 2018) %>%
  group_by(time, auditc) %>%
  count()

cv$auditc <- as.factor(cv$auditc)

ggplot(cv, aes(x = time, y = n, group = auditc, color = auditc)) +
  geom_line() +
  labs(title = 'AUDITC - Cross-Validation Batch 1') +
  ylab('Counts')
```

### 2023-07-11 minos/validation/cross_validation_default.Rmd
Added a section for alcohol to both handovers and cross_validation_default notebooks
Added alcohol to the physical wellbeing model and module, and updated handovers and cross_validation with more plots

# SF_12

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12')
multi_year_boxplots(raw, cv, 'SF_12')
snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2014, 2016, 2018, 2020))
q_q_comparison(raw, cv, 'SF_12')
```
```{r}
sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2014)
print(sf12.14)
```
```{r}
sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2016)
print(sf12.16)
```
```{r}
sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2018)
print(sf12.18)
```
```{r}
sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2020)
print(sf12.20)
rm(sf12.14, sf12.16, sf12.18, sf12.20)
```

@@

>>>>

# SF_12_MCS

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_MCS')
multi_year_boxplots(raw, cv, 'SF_12_MCS')
snapshot_OP_plots(raw, cv, 'SF_12_MCS', target.years = c(2014, 2016, 2018, 2020))
q_q_comparison(raw, cv, 'SF_12_MCS')
```
```{r}
sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2014)
print(sf12.14)
```
```{r}
sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2016)
print(sf12.16)
```
```{r}
sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2018)
print(sf12.18)
```
```{r}
sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2020)
print(sf12.20)
rm(sf12.14, sf12.16, sf12.18, sf12.20)
```

# SF_12_PCS

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_PCS')
multi_year_boxplots(raw, cv, 'SF_12_PCS')
snapshot_OP_plots(raw, cv, 'SF_12_PCS', target.years = c(2014, 2016, 2018, 2020))
q_q_comparison(raw, cv, 'SF_12_PCS')
```
```{r}
sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_PCS', 
                                 target.year = 2014)
print(sf12.14)
```
```{r}
sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_PCS', 
                                 target.year = 2016)
print(sf12.16)
```
```{r}
sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_PCS', 
                                 target.year = 2018)
print(sf12.18)
```
```{r}
sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_PCS', 
                                 target.year = 2020)
print(sf12.20)
rm(sf12.14, sf12.16, sf12.18, sf12.20)
```

@@

# Alcohol

```{r}
alc.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'auditc')

cv_ordinal_plots(pivoted.df = alc.pivoted, 
                 var = 'auditc',
                 save = FALSE)
rm(alc.pivoted)
```
